%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,letter]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%%
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font
%% folder.


% Change the page layout if you need to
% \geometry{left=1cm,right=10cm,marginparwidth=8.25cm,marginparsep=.75cm,top=0.5cm,bottom=1cm}
\geometry{left=1cm,right=8.8cm,marginparwidth=6.8cm,marginparsep=1cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[none]{hyphenat}
\usepackage[document]{ragged2e}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Black}{HTML}{000000}

\definecolor{LightGreen}{HTML}{90EE90}
\definecolor{AccentGreen}{HTML}{339966}
\definecolor{AcePurple}{HTML}{800080}
\definecolor{DarkerPurple}{HTML}{5b005b}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{SomeBlue}{HTML}{4286f4}

\colorlet{heading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Devin Jiang}
%\tagling{Seeking a Summer or Fall 2023 Data Engineering Co-op/Internship}
%\tagling{Seeking a Summer or Fall 2023 Software Engineering Co-op/Internship}
\tagline{Seeking a Summer 2024 Software Engineering Co-op/Internship}
\personalinfo{%
  \email{devinjiang7@gmail.com}
  \github{github.com/dj6207}
  \phone{(917) 530-8909}
  \linkedin{in/jiangdevin}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
% \marginpar{\makesidebarheader\input{sidebar.tex}}
%     \vspace*{-1\baselineskip}
\makecvheader
\end{fullwidth}

% \cvsection[sidebar]{Experience}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\medskip

\cvsection[sidebar]{Experience}

\cvexperience{\textbf{Baxter International | Test Engineering Intern}}{August 2023 - January 2024}{Skaneateles, NY}
\begin{itemize}
  \item Maintained and optimized automation scripts, enhancing reliability and performance, ensuring smoother operational workflows.
  % \item Implemented Python automation tools to perform data analysis, effectively organizing and presenting data in Excel sheets.
  \item Refactored and improved the existing Python code for the Dorna2 robotic arm, significantly improving reliability.
  \item Developed a desktop application for inventory tracking, ensuring efficient management of test fixtures and devices.
\end{itemize}
\textit{\textbf{Tools:} Python, Rust, Tauri, TypeScript, React, Material UI, Linux, Raspberry Pi}

\divider

\cvexperience{\textbf{Konfoong Materials International | Software Engineering Intern}}{July 2023 -- August 2023}{Yu Yao, China}
\begin{itemize}
  \item Collaborated effectively with another intern to design and develop a MVP for a home automation software from scratch.
  \item Successfully containerized and deployed the MVP on Alibaba Cloud IoT platform.
  \item Helped compose a Software Architecture documentation, providing a clear framework for future scalability and maintenance.
\end{itemize}
\textit{\textbf{Tools:} React, Redux Toolkit, TypeScript, Material UI, Docker, Alibaba Cloud}

\divider

\cvexperience{\textbf{Soleras Advanced Coatings | Software Engineering Intern}}{June 2023 -- August 2023}{Deinze, Belgium}
\begin{itemize}
  \item Transformed a manual Python analysis script into an automated service, increasing processing efficiency and reducing human error.
  \item Implemented a communication link utilizing the GRPC protocol to ensure seamless transfer of analyses between the Python service and the C\# backend.
  \item Enhanced the Angular frontend to display the analysis effectively to the operators.
\end{itemize}
\textit{\textbf{Tools:} Angular, TypeScript, NgRx,  C\#, Python, GRPC}

\medskip

\cvsection{Projects}

% \cvproject{\textbf{Watch Dog}}{\href{https://github.com/dj6207/AppTracker}{https://github.com/dj6207/AppTracker}}{Feb 2023 -- May 2023}
% \begin{itemize}
%   \item Developed a C\# WinForm application utilizing .NET 6.0 to track the time spent on desktop applications and display the collected data in a pie chart.
%   \item Deployed a SQLite database to store the time spent on applications.
% \end{itemize}
% \textit{\textbf{Tools:} C\#, SQLite, .NET 6.0}

\cvproject{\textbf{Watch Dog}}{\href{https://github.com/dj6207/watchdog}{https://github.com/dj6207/watchdog}}{Nov 2023 -- Present}
\begin{itemize}
  \item Developed a desktop application leveraging the Tauri Framework, designed to monitor and analyze user activity and application usage.
  \item Implemented the backend in Rust, ensuring efficient performance and secure data handling for real time activity monitoring.
  \item Utilized React to graph and visualize the collected data in real time.
\end{itemize}
\textit{\textbf{Tools:} Rust, TypeScript, SQLite, Tauri, React}

\divider

\cvproject{\textbf{The Bakery}}{\href{https://github.com/RIT-SWEN-261-04/team-project-2225-swen-261-04-c-bakery}{https://github.com/TheBakery}}{Jan 2023 -- May 2023}
\begin{itemize}
  \item Collaborated with a team of 4 to develop a website that sells baked goods using the Angular framework.
  \item Leveraged the REST API to effectively access and modify JSON files to build a database of products and users.
  \item Employed the Scrum software development cycle involving routine standups, sprint planning, and sprint retrospectives.
\end{itemize}
\textit{\textbf{Tools:} Java, TypeScript, Angular, REST API, Trello, Docker, Slack}

% \divider

% \cvproject{\textbf{Threo Bot}}{\href{https://github.com/dj6207/AutoGBF}{https://github.com/dj6207/AutoGBF}}{Nov 2022 -- Feb 2023}
% \begin{itemize}
%   \item Developed Threo bot, Python program utilizing YOLOv5 image recognition model for automating mouse clicks on specific images on the computer screen.
%   \item Trained a custom YOLOv5 image recognition model on the Google Cloud Compute Engine Platform using thousands of custom labeled data points.
% \end{itemize}
% \textit{\textbf{Tools:} Python, Google Compute Engine, YOLOv5}


\clearpage

\end{document}
