%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeListItems}[2]{
    \small{\textbf{#1}: #2}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Devin Jiang} \\ \vspace{1pt}
    \textbf{\large Seeking a Summer and Fall 2024 Software Engineering Co-op/Internship} \\
    917-530-8909 $|$ \href{mailto:devinjiang7@gmail.com}{\underline{devinjiang7@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/jiangdevin}{\underline{in/jiangdevin/}} $|$
    \href{https://github.com/dj6207}{\underline{github.com/dj6207}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Bachelor of Science in Computer Engineering; GPA: 3.7}{Expected Graduation: May 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Baxter International}{August 2023 - January 2024}
      {Test Engineering Intern}{Skaneateles, NY}
    \resumeItemListStart
        \resumeItem {Optimized automation scripts, enhancing reliability and performance, ensuring smoother operational workflows.}
        \resumeItem {Implemented Python automation tools to perform data analysis, effectively organizing data in Excel.}
        \resumeItem {Refactored and improved the existing Python code for the Dorna2 robotic arm, significantly improving reliability.}
        \resumeItem {Developed a desktop application for inventory tracking, ensuring efficient management of test fixtures and devices.}
    \resumeItemListEnd
    \resumeListItems{Tools}{Python, Rust, Tauri, TypeScript, React, Material UI, Linux, Raspberry Pi}

    \resumeSubheading
      {Konfoong Materials International}{July 2023 - August 2023}
      {Software Engineering Intern}{Yu Yao, China}
    \resumeItemListStart
        \resumeItem {Collaborated effectively with another intern to design and develop a MVP for a home automation software.}
        \resumeItem {Spearheaded the frontend development of the software utilizing React and Material UI for rapid development.}
        \resumeItem {Successfully containerized and deployed the MVP on Alibaba Cloud IoT platform.}
        \resumeItem {Composed a Software Architecture documentation, providing a framework for future scalability and maintenance.}
    \resumeItemListEnd
    \resumeListItems{Tools}{React, Redux Toolkit, TypeScript, Material UI, Docker, Alibaba Cloud}


    \resumeSubheading
      {Soleras Advanced Coatings}{June 2023 - August 2023}
      {Software Engineering Intern}{Deinze, Belgium}
    \resumeItemListStart
        \resumeItem {Transformed a manual Python analysis script into an automated service, increasing processing efficiency and reducing human error.}
        \resumeItem {Implemented a communication link utilizing the GRPC protocol to ensure seamless transfer of analysis data between the Python service and the C\# backend.}
        \resumeItem {Enhanced and updated the Angular frontend to display the analysis effectively to the operators.}
    \resumeItemListEnd
    \resumeListItems{Tools}{Angular, TypeScript, NgRx,  C\#, Python, GRPC}


  \resumeSubHeadingListEnd


% -----------PROJECTS-----------
\section{Projects}
   \resumeSubHeadingListStart
   \resumeProjectHeading
        {\textbf{ReFlick} $|$ \href{https://github.com/dj6207/BrickhackX}{https://github.com/dj6207/BrickhackX}}{}
        \resumeItemListStart
            \resumeItem {Developed a web application utilizing OpenAI to provide users with tailored recycling instructions based on uploaded images.}
            \resumeItem {Utilized Flask to make OpenAI API requests for image classification and generation of item recycling instructions.}
            \resumeItem {Deployed the web application through Vercel and hosted the backend on Heroku.}
        \resumeItemListEnd
    \resumeListItems{Tools}{React, OpenAI API, JavaScript, Flask, Python, Vercel, Heroku, Docker}
    \resumeProjectHeading
        {\textbf{Watch Dog} $|$ \href{https://github.com/dj6207/watchdog}{https://github.com/dj6207/watchdog}}{}
        \resumeItemListStart
            \resumeItem {Developed a desktop application leveraging Tauri, designed to monitor and analyze application usage.}
            \resumeItem {Implemented the Rust backend, ensuring efficient performance and secure data handling for real time monitoring.}
            \resumeItem {Utilized Recharts library to graph and visualize the collected data in real time.}
        \resumeItemListEnd
        \resumeListItems{Tools}{Rust, TypeScript, SQLite, Tauri, React}
   \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: Python, TypeScript, Rust, C, C\#, Java, HTML, CSS, SQL, React, Angular, Tauri} \\
     \textbf{Technologies}{: Git, Docker, SQLite, PostgreSQL, Linux, Raspberry Pi, Alibaba Cloud, Google Cloud Platform} \\
    }}
 \end{itemize}

 
%-----------ACTIVITIES SKILLS-----------
\section{Activities}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Computer Science House} $|$ \textit{Alumni}}{August 2021 - September 2022}
        \resumeItemListStart
            \resumeItem {Participated in weekly house meetings and technical seminars to learn new skills and concepts.}
            \resumeItem {Worked on various personal projects with guidance from technically experienced members.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}